\chapter{Algorithms and Implementation}
\label{chap:algorithms}

\section{DAG Evaluator}
\label{sec:alg:evaluator}

\TODO{Describe the inner-loop pass that walks the schedule DAG, applies
each operation to the current state, accumulates decoherence, and returns
the final $(\mathbf{e}, P_{\mathrm{success}}, T_{\mathrm{gen}})$ triple.
Explain validation against the three canonical closed-form benchmarks.}

\section{Brute-Force Search}
\label{sec:alg:bruteforce}

\TODO{Define the four fixed families
(\texttt{raw}, \texttt{end\_heralded}, \texttt{end\_optimistic},
\texttt{link\_level}, \texttt{flexible\_paper})
and the enumeration strategy. State the exact scope of what brute force
covers and its computational cost.}

\section{Dynamic-Programming Search}
\label{sec:alg:dp}

\TODO{Present the \texttt{SpanPartitionSearch} recursion: leaf-level
(per-hop link purification with variable copies and circuit sequence)
and recursive-level (join across disjoint sub-spans). Describe
Pareto-frontier pruning on $(\mathrm{cost}, F, P_{\mathrm{success}})$.}

\section{Heuristic Beam Search}
\label{sec:alg:beam}

\TODO{Describe the outer-loop beam search that extends the DP with
a configurable beam width. Motivate when it is needed (large $N$,
large budget) and its runtime complexity.}

\section{Cost Functions}
\label{sec:alg:cost}

\TODO{Define the two cost functions used to rank candidates:
$C_{\mathrm{fid}}$ (infidelity subject to throughput constraint) and
$C_{\mathrm{rate}}$ (effective rate subject to fidelity floor). Show how
each maps to one of the objectives from~\Cref{sec:model:objectives}.}

\section{Software Architecture}
\label{sec:alg:software}

\TODO{Brief description of the Python package \texttt{hrgs\_scheduler}:
module layout, key interfaces (\texttt{NetworkConfig}, \texttt{ScheduleDAG},
\texttt{ResourceBudget}), serialisation, and test coverage.}